Parallel Global Optimization for Non-Convex Mixed-Integer Problems

### 2019-10-01 2019/RSD_Integer/RSD2019.tex
Add two more references from SuperFRI

In this paper the global optimization problems and the method of their solving are
considered. The global optimization problems are the time-consuming ones since the global
optimum is an integral characteristic of the problem being solved and requires the investigation
of the whole search domain.
As a result, the search of the global optimum is reduced to the construction of a coverage (in
general, a nonuniform one) of the space of parameters. 
Such problems are common in applications \cite{Sulimov}.
The problems, in which some parameters can take the discrete or integer values only (\textit{mixed-integer global
optimization problems}) are of special interest because for these problems it is more difficult to build
the estimates of the optimum as compared to the continuous ones.

@@

@@

\bibitem{Sovrasov2019}
Sovrasov, V., Bevzuk, S.: Comparison of several sequential and parallel derivative-free global optimization algorithms. 	Communications in Computer and Information Science (2019) (article in press)

>>>>

In this paper the global optimization problems and the method of their solving are
considered. The global optimization problems are the time-consuming ones since the global
optimum is an integral characteristic of the problem being solved and requires the investigation
of the whole search domain.
As a result, the search of the global optimum is reduced to the construction of a coverage (in
general, a nonuniform one) of the space of parameters; 
such problems are common in applications \cite{Anisimov,Romanov,Sulimov}.
The problems, in which some parameters can take the discrete or integer values only (\textit{mixed-integer global
optimization problems}) are of special interest because for these problems it is more difficult to build
the estimates of the optimum as compared to the continuous ones.

@@

\bibitem{Anisimov}
Anisimov, K.S., Savelyev, A.A.,	Kursakov, I.A.,	Lysenkov, A.V.,	Prakasha, P.S.: Optimization of BWB aircraft using parallel computing. Supercomputing Frontiers and Innovations \textbf{5}(3), 93--97 (2018)

\bibitem{Romanov}
Romanov, S.Y.: Supercomputer simulations of nondestructive tomographic imaging with rotating transducers. Supercomputing Frontiers and Innovations \textbf{5}(3), 98--102 (2018)

@@

\bibitem{Sovrasov2019}
Sovrasov, V.: Comparison of several stochastic and deterministic derivative-free global optimization algorithms. 	Lecture Notes in Computer Science  \textbf{11548}, 70--81 (2019)
